Synthetic algebraic geometry and the phenomenon of nongeometric sequents

### 2018-04-07 slides-pssl103.tex
Final changes

  \begin{block}{\centering Definition}\small
  The \hil{big Zariski topos} $\Zar(S)$ is the
  category $\Sh(\Sch/S)$. It consists of functors
  $(\Sch/S)^\op \to \Set$ satisfying the gluing condition that
  \[ F(U) \to
    \prod_i F(U_i) \rightrightarrows
    \prod_{j,k} F(U_j \cap U_k) \]
  \\[-0.6em]
  is a limit diagram for any scheme~$U = \bigcup_i U_i$ over~$S$.
  \end{block}

  \begin{changemargin}{-1.0em}{-0.5em}
  \begin{itemize}
    \item For an~$S$-scheme~$X$, its functor of points $\ull{X} =
    \Hom_S(\cdot,X)$ is an object of~$\Zar(S)$. It feels like \hil{the set of
    points} of~$X$. \\[0.2em]
    \item \ \\[-1.2em]\mbox{In particular, there is the ring object $\affl$ with~$\affl(U) =
    \O_U(U)$.} \\[0.2em]
    \item $\Zar(S)$ classifies local~$\O_S$-algebras which are local
    over~$\O_S$.
  \end{itemize}
  \end{changemargin}
\end{frame}

@@

>>>>

  \begin{block}{\centering Definition}\small
  The \hil{big Zariski topos} $\Zar(S)$ is the
  category $\Sh(\Sch/S)$. It consists of functors
  $(\Sch/S)^\op \to \Set$ satisfying the gluing condition that
  \[ F(T) \to
    \prod_i F(U_i) \rightrightarrows
    \prod_{j,k} F(U_j \cap U_k) \]
  \\[-0.6em]
  is a limit diagram for any scheme~$T = \bigcup_i U_i$ over~$S$.
  \end{block}

  \begin{changemargin}{-1.0em}{-0.5em}
  \begin{itemize}
    \item For an~$S$-scheme~$X$, its functor of points $\ull{X} =
    \Hom_S(\cdot,X)$ is an object of~$\Zar(S)$. It feels like \hil{the set of
    points} of~$X$. \\[0.2em]
    \item \ \\[-1.2em]\mbox{In particular, there is the ring object $\affl$ with~$\affl(T) =
    \O_T(T)$.} \\[0.2em]
    \item $\Zar(S)$ classifies local~$\O_S$-algebras which are local
    over~$\O_S$.
  \end{itemize}
  \end{changemargin}
\end{frame}

@@

\section{Further research}

\begin{frame}{Further research}
  \vspace*{-1em}
  \small
  \begin{itemize}
    \item Push synthetic algebraic geometry further:
          true cohomology, intersection theory, derived categories, \ldots
          \\[-1.9em]

    \item What do the various subtoposes of~$\Zar(S)$ classify
          (étale, fppf, ph, $\neg\neg$, \ldots)? What about the crystalline
          topos?
          \\[-1.9em]

    \item Understand quasicoherence.
          \\[-1.9em]

    \item Find further applications of nongeometric sequents, for instance in
    constructive algebra.
  \end{itemize}

  {\vspace{-0.1em}\centering
  \rotatebox{90}{\tiny\scalebox{0.5}{Illustration: Carina Willbold}}\hspace{-0.05cm}%
  \includegraphics[scale=0.18]{images/external-internal-small}
  \par\medskip\vspace{-0.5em}}

  \centering
  Expository notes: \\
  \hil{\href{https://www.ingo-blechschmidt.eu/}{https://www.ingo-blechschmidt.eu/}}
  \par
\end{frame}
